The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-29 paper/ms.tex
editada parte de finkelstein

The information in that study comes from the ACS and WFC3/IR using the
filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
$J{125}$,  $JH_{140}$ and $H_{160}$.
The study inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.  
The total area  at redshift 6 corresponds to 740.8 arcmin$^2$ over
five different lines of sight, with a total estimated volume of  $1.8 \times
10^6 \textrm{Mpc}^3$ comoving.

The limit magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
$\sim30 $mag in  the  deepest field (XDF). 
The total number of $z=6$ LBG candidates is $940$, most of 
them in the faint end of the LF given the relativeley small survey volume.
The restframe UV magnitudes for these candidates are in the range.
$-22.52\leq M_{1600} \leq -16.77$.
\citet{Bouwens15} estimated the Luminosity Function (LF) using a 
stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
They obtained the following Schechter parameters:
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{Bouwens15} notes that only using few fields of view can yield a
LF with a deviations from the Schechter shape.

\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS 
fields, along with two of the Hubble Frontier Fields (HFF) of deep parallel 
observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 
clusters. 
The HFF uses the ACS and the WFC3/IR with the same filters
aforementioned but $z_{850}$. Total survey area is around  
$\sim300\textrm{arcmin}^2$, with 706 photometric candidates at redshift 6 
defined as the interval $5.5<z<6.5$. Total volume of this study is around 
$ 8 \times 10^5 \textrm{Mpc}^3$. The Schechter function parameters they found 
are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.

>>>>

The information in that study comes from the ACS and WFC3/IR using the
filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
$J{125}$,  $JH_{140}$ and $H_{160}$.
The study inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS, with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.

The total survey area is $740.8$ arcmin$^2$ over five different lines
of sight, with a total estimated volume of  $1.8 \times 10^6
\textrm{Mpc}^3$ comoving. 
The limiting magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
$\sim30 $mag in  the  deepest field (XDF). 
The total number of $z=6$ LBG candidates is $940$, most of 
them in the faint end of the LF given the relativeley small survey volume.
The restframe UV magnitudes for these candidates are in the range.
$-22.52\leq M_{1600} \leq -16.77$.
\citet{Bouwens15} estimated the Luminosity Function (LF) using a 
stepwise maximum-likelihood (SWML) based on \citet{Efstathiou88}. 
They obtained the following Schechter parameters:
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
\citet{Bouwens15} notes that only using few fields of view can yield a
LF with a deviations from the Schechter shape.

\citet{Finkelstein14} worked also with HST, using the HUDF, CANDELS and GOODS 
fields, along with two of the Hubble Frontier Fields (HFF) of deep parallel 
observations (unlensed fields) near the Abell 2744 and MACS J0416.1-2403 
clusters. 
The HFF uses the ACS and the WFC3/IR with the same filters
aforementioned except $z_{850}$.

The total survey area is around   $\sim300\textrm{arcmin}^2$ with a
total estimated volume of $8\times 10^5$ Mpc$^{-3}$.
There are 706 photometric candidates at redshift 6  defined as the
interval $5.5<z<6.5$. 
The Schechter function parameters estimated for this data set 
are $\phi^* =(1.86_{-0.80}^{+0.94}) \times 10 ^{-4}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.1_{-0.31}^{+0.25}$ and $\alpha = -2.02_{-0.10}^{+0.10}$.
